### 2024-04-27 author-kit-CVPR2024-v2/sec/1_intro.tex
PT bibliography and citations

\indent Over 50 million Americans seek physical therapy every year, whether that be from 
musculoskeletal conditions, car accidents, or sports injuries. Evidently, there is a large
need for physical therapy. However, only 35% of PT patients actually adhere to their assigned 
plan. This is a significant problem since the majority of patients are not following 
through with their exercises and thus decrease the effectiveness of their therapy plan.
\\
\indent We aim to use Computer Vision to partition each exercise movement into more easily digestible chunks 
by creating a model that can learn (vectorize) each exercise movement from two given videos, an instructional 
one and a patient one, and compare the two. By developing a tool that provides feedback as a result of analyzing 
the two videos, which ideally should match perfectly, adhering to an exercise plan 
becomes much more feasible, enjoyable, and even motivating.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
\indent Several existing attempts have been made to tackle the challenge of improving patient adherence, 
each with its own approach and limitations. One such approach involves utilizing monitoring technology, 
such as pedometers, which have proved to be user-friendly. Though such monitoring technologies are 
able to monitor, or track, the patients' physical activity decently well, there was not much of an effect in terms 
of improving their adherence to their exercise plans. As a result, patients using such technologies still struggle with 
adhering to their exercise plans.
\\
\indent Another attempt that has been made is virtual and augmented reality treatment. Through this method, patients 
are able to put on their VR headsets and transport into any environment they would like to complete their exercises in. 
The possibilities are endless: they could surround themselves in peaceful, serene nature, or they could 
opt for a more competitive gaming atmosphere. Physical therapists have found that this actually 
makes their treatment plans more appealing and thus improves their patient adherence rates. However, 
it is important to note that this is significantly more expensive. The cost associated with this 
method is typically too high for the majority of patients and thus makes this approach less practical.
\\
\indent Unlike the aforementioned methods, our proposed method is low-cost, accessible, and effective. 
Implementing the aspect of gamification allows for physical therapy to be fun yet productive. Patients become 
competitors, working hard to beat their previous scores. Additionally, our method could be expanded to offer 
further personalized feedback based on the analysis of the learner's own video and the given instructional video, 
ideally without the requirement for perfect lighting or camera angle conditions.

>>>>

\indent Over 50 million Americans seek physical therapy every year, whether that be from 
musculoskeletal conditions, car accidents, or sports injuries. Evidently, there is a large
need for physical therapy\cite{Authors14i}. However, only 35% of PT patients actually adhere to their assigned 
plan\cite{Authors14h}. This is a significant problem since the majority of patients are not following 
through with their exercises and thus decrease the effectiveness of their therapy plan.
\\
\indent We aim to use Computer Vision to partition each exercise movement into more easily digestible chunks 
by creating a model that can learn (vectorize) each exercise movement from two given videos, an instructional 
one and a patient one, and compare the two. By developing a tool that provides feedback as a result of analyzing 
the two videos, which ideally should match perfectly, adhering to an exercise plan 
becomes much more feasible, enjoyable, and even motivating.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
\indent Several existing attempts have been made to tackle the challenge of improving patient adherence, 
each with its own approach and limitations. One such approach involves utilizing monitoring technology, 
such as pedometers, which have proved to be user-friendly. Though such monitoring technologies are 
able to monitor, or track, the patients' physical activity decently well, there was not much of an effect in terms 
of improving their adherence to their exercise plans\cite{Alpher10}. As a result, patients using such technologies still struggle with 
adhering to their exercise plans.
\\
\indent Another attempt that has been made is virtual and augmented reality treatment. Through this method, patients 
are able to put on their VR headsets and transport into any environment they would like to complete their exercises in. 
The possibilities are endless: they could surround themselves in peaceful, serene nature, or they could 
opt for a more competitive gaming atmosphere. Physical therapists have found that this actually 
makes their treatment plans more appealing and thus improves their patient adherence rates\cite{Authors14j}. However, 
it is important to note that this is significantly more expensive. The cost associated with this 
method is typically too high for the majority of patients and thus makes this approach less practical.
\\
\indent Unlike the aforementioned methods, our proposed method is low-cost, accessible, and effective. 
Implementing the aspect of gamification allows for physical therapy to be fun yet productive. Patients become 
competitors, working hard to beat their previous scores. Additionally, our method could be expanded to offer 
further personalized feedback based on the analysis of the learner's own video and the given instructional video, 
ideally without the requirement for perfect lighting or camera angle conditions.
